\cleardoublepage
%\pagebreak
\phantomsection
\addcontentsline{toc}{chapter}{Bibliographie}
\begin{thebibliography}{99}

\bibitem{low99} David G. Lowe, \emph{Object Recognition from Local Scale-Invariant Features,} In proceeding of the 7th International conference of computer vision, pages 1150 - 1157, Corfou, Grèce, 1999.

\bibitem{sss07} Shalev-Shwartz, S.Singer, Y.Srebro, \emph{Primal esti-mated sub-gradient solver for svm.}, Proceedings of the Twenty-Fourth International Conference Machine Learning. pp. 807–814, ACM (2007).

\bibitem{svmdatamul}\emph{LIBSVM Data : Classification (Multi-class)},\ \url{<http://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/multiclass.html}

\bibitem{khang09} PHAM Nguyen Khang, \emph{Analyse factorielle des correspondances pour l'indexation et la recherche d'information dans une grande base de données d'image}, thèse IRISA, 2009.

\bibitem{sm97} C.Schmid and R.Mohr, \emph{Local Greyvalue Invariants for Image Retrieval}, IEEE Transactions on Pattern Analysis and Machine Intelligence,530--534, 19, 5 (1997).

\bibitem{hs88} Chris Harris and Mike Stephens, \emph{A combined corner and edge de detector},  in Alvey Vision Conf., 1988, pp. 147 - 151.

\bibitem{dsh00} Y.Dufournaud, C.Schmid and R.Horaud, \emph{Matching Images with Different Resolutions}, in "International Conference on Computer Vision and Pattern Recognition (CVPR '00) 1 (2000) 612--618"

\bibitem{lin98} Tony Lindeberg, \emph{Feature Detection with Automatic Scale Selection,} Technical report ISRN KTH/NA/P–96/18–SE, May 1996, Revised August 1998. Int. J. of Computer Vision, vol 30, number 2, 1998. (In press).

\bibitem{nk13} T-N DO, N-K PHAM, \emph{Phan lop anh voi giai thuat giam gradient ngau nhien da lop,} Magasin Cantho university, 29 (2013).

\bibitem{ms01} K.Mikolajczyk and C.Schmid, \emph{Indexing based on scale invariant interest points}, in "Computer Vision, 2001. ICCV 2001. Proceedings. Eighth IEEE International Conference on  (Volume:1 )", pages 525 - 531, 2001.

\bibitem{low04} David G. Lowe, \emph{Distinctive Image Features from Scale-Invariant Keypoints}, International journal of computer vision, 60(2), 91 - 110, 2004.

\bibitem{bmp02} S.Belongie, J.Malik and J.Puzicha, \emph{Shape matching and object recognition using shape contexts}, in "Pattern Analysis and Machine Intelligence, IEEE Transactions on  (Volume:24 ,  Issue: 4 )", pages 509 - 522, 2002.

\bibitem{ks04} Yan Ke and Rahul Sukthankar, \emph{PCA-SIFT: A More Distinctive Representation for Local Image Descriptors}, in "Computer Vision and Pattern Recognition", 2004.

\bibitem{ms05} K.Mikolajczyk and C.	Schmid, \emph{A performance evaluation of local descriptors}, in "Pattern Analysis and Machine Intelligence, IEEE Transactions on  (Volume:27 ,  Issue: 10 )", 2005.

\bibitem{mt10} Marco Treiber, \emph{An introduction to object recognition: selected algorithms for a wide variety of application}, ISBN 9781849962346, pages p. 147, 2010.

\bibitem{jm67} J.MacQueen, \emph{Some methods for classification and analysis of multivariate observations. Proceedings of 5th Berkeley Symposium on Mathematical Statistics and Probability}, Berkeley, University of California Press Vol.1, pp. 281-297 (1967).

\bibitem{jp98} J.Platt, \emph{Sequential Minimal Optimization: A Fast Algorithm for Training Support Vector Machines}, Microsoft Research Technical Report MSR-TR-98-14 (1998).

\bibitem{cl01} C.Chang and C.Lin, \emph{LIBSVM – a library for support vector machines}, http://www.csie.ntu.edu.tw/~cjlin/libsvm (2001).

\bibitem{ww99} J.Weston, C.Watkins\emph{Support vector machines for multi-class pattern recognition.}, Proceedings of the Seventh European Symposium on Artificial Neural Networks. pp. 219–224. (1999)

\bibitem{vv95} V.Vapnik, \emph{The Nature of Statistical Learning Theory.}, Springer, New York (1995).

\bibitem{vv82} V.Vapnik, et S. Kotz \emph{Estimation of Dependences Based on Empirical Data,} Springer Series in Statistics, 1982, ISBN 978-0387907338.

\bibitem{uk99} U.Krebel, \emph{Pairwise classification and support vector machines}, Support Vector Learning, Advances in Kernel Methods. pp.255–268. (1999).

\bibitem{bos07} A.Bosch, A.Zisserman and X.Munoz \emph{Scene
classification via pLSA.}, Proceedings of the European Conference on Computer Vision, pp. 517–530 (2006).

\bibitem{mq67} J.MacQueen \emph{Some methods for classification and analysis of multivariate observations.}, Proceedings of 5th Berkeley Symposium on Mathematical Statistics and Probability, Berkeley, University of California Press Vol.1, pp. 281-297 (1967).

\bibitem{khang} Nguyen-Khang Pham http://www.cit.ctu.edu.vn/~pnkhang/index-en.html, Can Tho University

\bibitem{svmdata1}\emph{LIBSVM Data: Classification (Binary Class)},\ \url{http://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/binary.html}

%\bibitem{ms02} K.Mikolajczyk, Detection of local features invariant to affine transformations, Ph.D. thesis, Institut National Polytechnique de Grenoble, France, 2002.

%\bibitem{yg07} J.Weston, C.Watkins\emph{Svm multiclasses.}, théorie et applications (2007)

\end{thebibliography}
